The paper on \Large \bf Blockchain Frontrunning

### 2018-09-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Notes from the meeting

\section{Introduction}
The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started. Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few decades, trading is not happening in person anymore and a greater number of applications are now vulnerable to front-running. Furthermore, Blockchain technology has introduced transparency and open markets which led to a new threat of front-running and it inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain. However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study. There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases.\footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}

%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%
%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .

@@

%TODO: fix the table! 
\input{setup/table}

@@

\section{How to stop Front-running?}
In the traditional markets, front-running is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

>>>>

\section{Introduction}

The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started. Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few decades, trading is not happening in person anymore and a greater number of applications are now vulnerable to front-running. Furthermore, Blockchain technology has introduced transparency and open markets which led to a new threat of front-running and it inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain. However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study. There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases. \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention". }

%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
% Why is this important.
% PAPER BEING SOLD HERE
%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}

%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions. Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them. We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models. Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial. Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place. In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues. While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.

%______________________________________________________________%
%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .

@@

%TODO: fix the table!  %mahsa: add MISC back to the table! %%%% put a seperate cell for name services and put the ENS
% Mention that the categories were taken from that website (Dapp.com) OR recategorize categorize the table

\input{setup/table}

@@

\section{How to stop Front-running?} %We have have the applicability of the solutions inline.

In the traditional markets, front-running is considered unethical and also illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for unethical behaviour, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

### 2018-09-06 frontrunning/Latex/setup/table.tex
[frontrunning] Edits on the top 25 Dapps table
[frontrunning] Notes from the meeting

\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
												& Ethermon(4)\\
												& Cryptogirl (9)\\
												& Gods Unchained TCG (12)\\
												& Blockchain Cuties(15)\\
												& ETH.TOWN! (16)\\
												& 0xUniverse (18)\\
												& MLBCrypto Baseball (19)\\
												& HyperDragons(25)\\ \hline

\multirow{6}{*}{Gambling}								& Fomo3D (5) \\  
												& DailyDivs (6) \\ 
												& FomoWar (10) \\
												& FairDapp (11)\\
												& Zethr(17) \\
												& dice2.win (20) \\
												& Kyber (22) \\  \hline
\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
\end{table}
% ------------------------------------------------------------------------------------------------------------------------------------------------%

>>>>

\multirow{9}{*}{\shortstack{Crypto-Collectible \\ Games \\ (ERC 721)}}		& \textbf{CryptoKitties (3)} \\  
															& Ethermon(4)\\
															& Cryptogirl (9)\\
															& Gods Unchained TCG (12)\\
															& Blockchain Cuties(15)\\
															& ETH.TOWN! (16)\\
															& 0xUniverse (18)\\
															& MLBCrypto Baseball (19)\\
															& HyperDragons(25)\\ \hline

\multirow{6}{*}{Gambling}											& Fomo3D (5) \\  
															& DailyDivs (6) \\ 
															& FomoWar (10) \\
															& FairDapp (11)\\
															& Zethr(17) \\
															& dice2.win (20) \\
															& Kyber (22) \\  \hline

\multirow{2}{*}{\shortstack{High-Risk \\ (Ponzi Schemes and Lotteries)}}		& PoWH 3D (8)	 \\ 
															& Ether Shrimp Farm(21) \\  \hline

\multirow{2}{*}{Misc}												& 0x Protocol (23) \\
															& \textbf{Ethereum Name Service (24)}  \\  \hline

\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
\end{table}
% ------------------------------------------------------------------------------------------------------------------------------------------------%
